---
title: "Assignment 3"
author: "Jason Lim"
date: "2/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(leaflet)
```

## **Introduction**
In today's society, where the topic of racial disparity is often overlooked, many
racial and ethnic minorities are faced with challenges given by the country's flawed
criminal justice system. It is a widely known fact that people of color tend to
receive a longer sentence than white Americans and are also easily convicted, which
has left a tremendous fear to those people of color today. From this assignment, 
I hope to address such prevalent issue by creating multiple visualizations that 
display patterns of racial inequality existing in the prison system. The variables 
I'm choosing to analyze are geography, admission rate to both jail and prison,
and further investigate the demographics to observe if there's any patterns that infer
racial discrimination of the incarceration system. 

## **5 Values Relevant To The Topic**
Using the data frame from Vera Institute, I found some key values that will help me
visualize better for my analysis.

* In 2016, the average prison admission rate for Asian is 19%, 1106% for black, 247% for Latinx,
530% for Native, and 335% for white.
* In 2016, the average jail population rate for Asian is 580%, 2527% for black, 1038% for Latinx,
1341% for Native, and 476% for white.
* Top five states with the highest black prison admission count are Illinois, California, 
Texas, New York, Maryland respectively. 
* In 2018, the total black jail population was 247547, and the total white jail population
was 346061.
* In 2018, the total black population was 28834577, and the total white population was 128996635.

## **Trends Over Time Chart**
_Description_: This stacked bar chart shows the average prison admission rate for each race over time from 2000 and 2018. 
By having a stacked bar chart, we can observe how the rate of each race change over time with clear visuals. 
It is evident that the rate for black is significantly larger than other race, and another thing to note is that
there is a significant change in rate for Latin around 2005 whereas the rate for others stayed constant. 
```{r chart 1, echo = FALSE}
source("../source/analysis.R")
plot(chart_one)
```

## **Variable Comparison Chart**
_Description_: For the comparison part, I used bar chart to compare the ratio of population of jail 
to total population for black and white. This gives clear visualization that the ratio for black outweigh
the ratio of white by almost 3 times. Though it doesn't directly infer the prevalence of racial discrimination
in criminal justice system, this is something to be looked into. 
```{r chart 2, echo = FALSE}
plot(chart_two)
```

## **Map**
_Description_:
```{r map, echo = FALSE}

```